\Rpackage{MSnbase}: labelled MS2 data pre-processing, visualisation and quantification.

### 2012-04-19 inst/doc/MSnbase-demo/MSnbase-demo.Rnw
Misc changes
CHANGES IN VERSION 1.5.1
-------------------------
 o updated NA warning message in readIspyData <2012-03-05 Mon>
 o fixed combineFeatures/combineMatrixFeatures for 1 sample <2012-03-20 Tue>
 o image method for MSnSet instances <2012-03-20 Tue>
 o fixed bug in plotNA (first t was wring) <2012-03-21 Wed>
 o import plot from stats4 <2012-03-21 Wed>
 o using reshape2 <2012-03-30 Fri>




git-svn-id: https://hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/MSnbase@64784 bc3139a8-67e5-0310-9ffc-ced21a209358
new version 1.5.2
CHANGES IN VERSION 1.5.2
-------------------------
 o tran

<<environment,cache=FALSE,echo=FALSE>>=
library("MSnbase")
library("grid")
library("reshape")
@

@@

<<quantify,echo=TRUE,cache=FALSE,keep.source=T>>=
qnt <- quantify(experiment,
                method = "trap",
                reporters = iTRAQ4,
                strict = FALSE,
                verbose = FALSE)
qnt
head(exprs(qnt))
@

@@

<<incompdiss,echo=TRUE,cache=FALSE,keep.source=T>>=
iTRAQ5
incompdiss <- quantify(itraqdata,
                       method = "trap",
                       reporters = iTRAQ5,
                       strict = FALSE,
                       verbose = FALSE)
head(exprs(incompdiss))
@

>>>>

<<environment,cache=FALSE,echo=FALSE>>=
library("MSnbase")
library("grid")
library("reshape2")
@

@@

<<quantify,echo=TRUE,cache=FALSE,keep.source=T>>=
qnt <- quantify(experiment,
                method = "trap",
                reporters = iTRAQ4,
                strict = FALSE,
                parallel = FALSE,
                verbose = FALSE)
qnt
head(exprs(qnt))
@

@@

<<incompdiss,echo=TRUE,cache=FALSE,keep.source=T>>=
iTRAQ5
incompdiss <- quantify(itraqdata,
                       method = "trap",
                       reporters = iTRAQ5,
                       strict = FALSE,
                       parallel = FALSE,
                       verbose = FALSE)
head(exprs(incompdiss))
@
